`State and Parameter Estimation for Spatio-Temporal Neural Fields' or `A Data Driven Framework for Patient-Specific Neural Field Modelling'

### 2010-06-17 ltx/Journal of Neuroengineering/StateAndParameterEstimationNeuralFields_JoNE.tex
completed table8

\begin{table}[h!]\footnotesize
    \begin{tabular}{ll}
        $\hat{\mathbf{x}}$ & State estimate \\
	$\chi$ & Matrix of sigma vectors \\
    	$\hat{\mathbf{x}}_t^{f-}$ & Forward prior estimate \\
    	$\hat{\mathbf{x}}_t^f$ & Forward posterior estimate \\
    	$\hat{\mathbf{x}}_t^{b-}$ & Backward prior estimate \\
    	$\hat{\mathbf{x}}_t^{b}$ & Backward posterior estimate \\
    	$P^f_t$ & Forward posterior covariance matrix \\
    	$P^{f-}_t$ & Forward prior covariance matrix \\
    	$P^b_t$ & Backward posterior covariance matrix \\
    	$P^{b-}_t$ & Backward prior covariance matrix \\
	$\mathcal K_{t} $& Filter gain\\
	$M_t$& Cross-covariance matrix\\
	$S_t$& Smoother gain
    \end{tabular}
    \caption{State Estimation}
\end{table}

>>>>

\begin{table}[h!]\footnotesize
    \begin{tabular}{ll}
        $\hat{\mathbf{x}}$ & State estimate \\
	$\chi$ & Matrix of sigma vectors \\
	$\lambda$& Scaling parameter\\
	$\alpha$& Determines the spread of sigma points\\
	$\beta$& Priro knowledge of the sigma points distribution\\
	$\kappa$& Scaling parameter\\
	$W$& Sigma vecors weights\\
    	$\hat{\mathbf{x}}_t^{f-}$ & Forward prior estimate \\
    	$\hat{\mathbf{x}}_t^f$ & Forward posterior estimate \\
    	$\hat{\mathbf{x}}_t^{b-}$ & Backward prior estimate \\
    	$\hat{\mathbf{x}}_t^{b}$ & Backward posterior estimate \\
    	$P^f_t$ & Forward posterior covariance matrix \\
    	$P^{f-}_t$ & Forward prior covariance matrix \\
    	$P^b_t$ & Backward posterior covariance matrix \\
    	$P^{b-}_t$ & Backward prior covariance matrix \\
	$\mathcal K_{t} $& Filter gain\\
	$M_t$& Cross-covariance matrix\\
	$S_t$& Smoother gain
    \end{tabular}
    \caption{State Estimation}
\end{table}
